Broad characteristics

### 2019-02-25 analysis/broad_characteristics.rmd
upd

```{r}
library(mrever)
connect()
library(dplyr)
library(data.table)
library(knitr)
library(ggplot2)

@@

## 2.

>>>>

```{r}
library(mrever)
connect()
library(dplyr)
library(data.table)
library(knitr)
library(ggplot2)
library(tidyr)

@@

## 2. Instrument selection

library(data.table)
library(dplyr)
library(tidyr)
library(mrever)
library(ggplot2)
connect()

b <- subset(o, method %in% c("FE IVW", "Wald ratio", "Steiger null"))

traits <- get_traits() %>% dplyr::select(c(bgcidId, sample_size, trait, nsnp))
out <- group_by(b, exposure, outcome, selection) %>% 
summarise(instruments = first(nsnp)) %>% 
inner_join(., traits, by=c("exposure"="bgcidId"))

p <- tidyr::spread(o, key=selection, value=instruments)

save(out, file="out.rdata")

ggplot(out, aes(x=sample_size, y=instruments)) +
# geom_point(aes(colour=selection)) +
geom_smooth(aes(colour=selection))

out$n2 <- out$sample_size
out$n2[out$n2 > 500000] <- NA

out$nbin <- cut(out$n2, 10)
table(out$nbin)

ggplot(subset(out, !is.na(n2)), aes(x=nbin, y=instruments)) +
geom_boxplot(aes(fill=selection), position="dodge", outlier.shape=NA) +
scale_fill_brewer(type="qual") +
theme(axis.text.x=element_text(angle=90))

temp <- subset(out, selection %in% c("DF", "Tophits")) %>% 
group_by(exposure, outcome) %>%
summarise(nrev = abs(diff(instruments)))

temp <- tidyr::spread(out, key=selection, value=instruments)
temp$nrev <- temp$Tophits - temp$DF
summary(lm(nrev ~ I(n2/10000), temp))

## Import result:

temp$prev <- temp$nrev / temp$Tophits
summary(lm(prev ~ I(n2/100000), temp))
summary(temp$prev)

# Across 758955 MR analyses, for every 100k increase in sample size the proportion of instruments that are reverse causal increases by 2.8% (s.e. 0.023, p < 2e-16)

ggplot(temp, aes(x=n2, y=prev)) +
geom_point(alpha=0.4) +
geom_smooth() +
geom_smooth(method="lm")

ggplot(temp %>% filter(!is.na(n2)), aes(x=nbin, y=prev)) +
geom_boxplot()

temp2 <- group_by(temp, exposure, n2) %>%
summarise(
	mdf = mean(Tophits - DF), pmdf = mdf / max(Tophits),
	mhf = mean(Tophits - HF), pmhf = mhf / max(Tophits)
)

summary(lm(pmdf ~ n2, temp2))
summary(lm(pmhf ~ n2, temp2))

ggplot(temp2 %>% , aes(x=))

summary(lm(nrev ~ I(n2/1000), temp))
